Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-04-17 HGmodelMANUSCRIPT/HGmodel_ACStemplate.tex
update authors

\author{Alexandru Botan}
%\affiliation{The authors are listed in alphaphetical order.}
%\affiliation{The author list is not completed.}
\affiliation[Lyon CNRS]{Institut Lumi\`ere Mati\`ere, UMR5306 Universit\'e Lyon 1-CNRS, Universit\'e de Lyon 69622 Villeurbanne, France}
%
%\author{Andrea Catte}
%\affiliation{University of East Anglia, Norwich, United Kingdom}
\author{Fernando Favela-Rosales}
\affiliation[Mexico]{Departamento de F\'isica, Centro de Investigaci\'on y de Estudios Avanzados del IPN, Apartado Postal 14-740, 07000 M\'exico D.F., M\'exico}
\author{Patrick F. J. Fuchs}
\affiliation[CNRS Paris]{Institut Jacques Monod, CNRS, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, Paris, France}
%\alsoaffiliation[Diderot University]
%{Institut Jacques Monod, CNRS UMR 7592, Universit{\'e} Paris Diderot, Sorbonne Paris Cit{\'e}, Paris, France}
\author{Matti Javanainen}
\affiliation[Tampere University of Technology]
{Department of Physics, Tampere University of Technology, Tampere, Finland}
\author{Matej Kandu\v{c}}
\affiliation[Freie Universit\"{a}t Berlin] 
{Fachbereich Physik, Freie Universitat Berlin, Berlin, Germany}
\author{Waldemar Kulig}
\affiliation[Tampere University of Technology]
{Department of Physics, Tampere University of Technology, Tampere, Finland}
\author{Antti Lamberg}
\affiliation[Kyoto University]
{Department of Chemical Engineering, Kyoto University, Kyoto, Japan}
\author{Claire Loison}
\affiliation[Lyon CNRS]{Institut Lumi\`ere Mati\`ere, UMR5306 Universit\'e Lyon 1-CNRS, Universit\'e de Lyon 69622 Villeurbanne, France}
\author{Markus S. Miettinen}
\affiliation[Freie Universit\"{a}t Berlin] 
{Fachbereich Physik, Freie Universitat Berlin, Berlin, Germany}
\author{Luca Monticelli}
\affiliation[UMR] 
{5IBCP, CNRS UMR 5086, Lyon, France}
\author{Jukka M{\"a}{\"a}tt{\"a}}
\affiliation[Aalto University]
{Aalto University, Espoo, Finland}
\author{O. H. Samuli Ollila} 
\email{samuli.ollila@aalto.fi.}
\affiliation[Aalto University]
{Aalto University, Espoo, Finland}
\author{Marius Retegan}
\affiliation[Max Planck]
{Max Planck Institute for Chemical Energy Conversion, Mulheim an der Ruhr, Germany}
\author{Tomasz Rog}
\affiliation[Tampere University of Technology]
{Department of Physics, Tampere University of Technology, Tampere, Finland}
\author{Hubert Santuz}
\affiliation[INSERM]
{INSERM, UMR\_S 1134, DSIMB, Paris, France}
\alsoaffiliation[Diderot]
{Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, UMR\_S 1134, Paris, France}
\alsoaffiliation[INTS]
{Institut National de la Transfusion Sanguine (INTS), Paris, France}
\alsoaffiliation[Labex]
{Laboratoire d'Excellence GR-Ex, Paris, France}
\author{Joona Tynkkynen}
\affiliation[Tampere University of Technology]
{Department of Physics, Tampere University of Technology, Tampere, Finland}

@@

@@

\subsection{Author Contributions}
\todo{Please write a text summarizing your contribution} \\
{\it Alexandru Botan} provided simulation results for charmm36-UA\\
{\it Fernando Favela} prepared, performed and analyzed simulations
with popc and cholesterol for the CHARMM36 All-Atom FF. \\
{\it Patrick F. J. Fuchs} Ran and analyzed the Poger simulations. Provided scientific information which significantly advanced the project (signs and forking of order parameters). \\
{\it Matti Javanainen} prepared and performed simulations with multiple lipid models and analyzed the results. Supervised the work of JT.\\
{\it Matej Kanduc} provided simulation results for the Berger DLPC model \\
{\it Waldemar Kulig} prepared the MD simulations with cholesterol for the MacRog FF \\
{\it Antti Lamberg}  \\
{\it Claire Loison} provided simulation results for charmm36-UA \\
{\it Markus S. Miettinen}  \\
{\it Luca Monticelli}  \\
{\it Jukka M{\"a}{\"a}tt{\"a}}  prepared and performed simulations with Berger and Slipids models and analyzed the results.\\
{\it O. H. Samuli Ollila} Designed and managed the work. Ran and analyzed several simulations. Wrote the manuscript.  \\
{\it Marius Retegan} Prepared and validated the GROMACS compatible parameter files for GAFFlipid and Lipid14 force fields.\\
{\it Tomasz Rog} Provided the topologies for the MacRog model and also the full hydration simulation data with this model. \\
{\it Hubert Santuz} prepared and performed the cholesterol simulations with CHARMM36 and analyzed the results. \\
{\it Joona Tynkkynen} prepared and performed the dehydration simulations with the MacRog FF.\\

>>>>

\author{Alexandru Botan}
%\affiliation{The authors are listed in alphaphetical order.}
%\affiliation{The author list is not completed.}
\affiliation[Lyon CNRS]{Institut Lumi\`ere Mati\`ere, UMR5306 Universit\'e Lyon 1-CNRS, Universit\'e de Lyon 69622 Villeurbanne, France}
%
%\author{Andrea Catte}
%\affiliation{University of East Anglia, Norwich, United Kingdom}
\author{Fernando Favela-Rosales}
\affiliation[Mexico]{Departamento de F\'isica, Centro de Investigaci\'on y de Estudios Avanzados del IPN, Apartado Postal 14-740, 07000 M\'exico D.F., M\'exico}
\author{Patrick F. J. Fuchs}
\affiliation[CNRS Paris]{Institut Jacques Monod, CNRS, Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, Paris, France}
%\alsoaffiliation[Diderot University]
%{Institut Jacques Monod, CNRS UMR 7592, Universit{\'e} Paris Diderot, Sorbonne Paris Cit{\'e}, Paris, France}
\author{Matti Javanainen}
\affiliation[Tampere University of Technology]
{Department of Physics, Tampere University of Technology, Tampere, Finland}
\author{Matej Kandu\v{c}}
\affiliation[Freie Universit\"{a}t Berlin] 
{Fachbereich Physik, Freie Universitat Berlin, Berlin, Germany}
\author{Waldemar Kulig}
\affiliation[Tampere University of Technology]
{Department of Physics, Tampere University of Technology, Tampere, Finland}
\author{Antti Lamberg}
\affiliation[Kyoto University]
{Department of Chemical Engineering, Kyoto University, Kyoto, Japan}
\author{Claire Loison}
\affiliation[Lyon CNRS]{Institut Lumi\`ere Mati\`ere, UMR5306 Universit\'e Lyon 1-CNRS, Universit\'e de Lyon 69622 Villeurbanne, France}
\author{Alexander Lyubartsev}
\affiliation[Stockholm University]
{Division of Physical Chemistry, Department of Materials and Environmental Chemistry, Stockholm University, S-106 91 Stockholm, SWEDEN}
\author{Markus S. Miettinen}
\affiliation[Freie Universit\"{a}t Berlin] 
{Fachbereich Physik, Freie Universitat Berlin, Berlin, Germany}
\author{Luca Monticelli}
\affiliation[IBCP] 
{Institut de Biologie et Chimie des Prot\'eines (IBCP), CNRS UMR 5086, Lyon, France}
\author{Jukka M{\"a}{\"a}tt{\"a}}
\affiliation[Aalto University]
{Aalto University, Espoo, Finland}
\author{O. H. Samuli Ollila} 
\email{samuli.ollila@aalto.fi.}
\affiliation[Aalto University]
{Aalto University, Espoo, Finland}
\author{Marius Retegan}
\affiliation[Max Planck]
{Max Planck Institute for Chemical Energy Conversion, Mulheim an der Ruhr, Germany}
\author{Tomasz Rog}
\affiliation[Tampere University of Technology]
{Department of Physics, Tampere University of Technology, Tampere, Finland}
\author{Hubert Santuz}
\affiliation[INSERM]
{INSERM, UMR\_S 1134, DSIMB, Paris, France}
\alsoaffiliation[Diderot]
{Universit\'e Paris Diderot, Sorbonne Paris Cit\'e, UMR\_S 1134, Paris, France}
\alsoaffiliation[INTS]
{Institut National de la Transfusion Sanguine (INTS), Paris, France}
\alsoaffiliation[Labex]
{Laboratoire d'Excellence GR-Ex, Paris, France}
\author{Joona Tynkkynen}
\affiliation[Tampere University of Technology]
{Department of Physics, Tampere University of Technology, Tampere, Finland}

@@

Luca Monticelli acknowledges funding proved by the Institut national de la sant\'e et de la recherche m\'edicale (INSERM).

@@

\subsection{Author Contributions}
\todo{Please write a text summarizing your contribution} \\
{\it Alexandru Botan} provided simulation results for charmm36-UA\\
{\it Fernando Favela} prepared, performed and analyzed simulations
with popc and cholesterol for the CHARMM36 All-Atom FF. \\
{\it Patrick F. J. Fuchs} Ran and analyzed the Poger simulations. Provided scientific information which significantly advanced the project (signs and forking of order parameters). \\
{\it Matti Javanainen} prepared and performed simulations with multiple lipid models and analyzed the results. Supervised the work of JT.\\
{\it Matej Kanduc} provided simulation results for the Berger DLPC model \\
{\it Waldemar Kulig} prepared the MD simulations with cholesterol for the MacRog FF \\
{\it Antti Lamberg}  \\
{\it Claire Loison} provided simulation results for charmm36-UA \\
{\it Alexander Lyubartsev} \\
{\it Markus S. Miettinen}  \\
{\it Luca Monticelli} Critical discussions in all phases of the project. Collaboration with Jukka  M{\"a}{\"a}tt{\"a}. \\
{\it Jukka M{\"a}{\"a}tt{\"a}}  prepared and performed simulations with Berger and Slipids models and analyzed the results.\\
{\it O. H. Samuli Ollila} Designed and managed the work. Ran and analyzed several simulations. Wrote the manuscript.  \\
{\it Marius Retegan} Prepared and validated the GROMACS compatible parameter files for GAFFlipid and Lipid14 force fields.\\
{\it Tomasz Rog} Provided the topologies for the MacRog model and also the full hydration simulation data with this model. \\
{\it Hubert Santuz} prepared and performed the cholesterol simulations with CHARMM36 and analyzed the results. \\
{\it Joona Tynkkynen} prepared and performed the dehydration simulations with the MacRog FF.\\
